---
title: "social-complexity-fd-nonfd-analyses"
format: html
---

```{r}
library(tidyverse)
library(brms)

ds_FA <- read_csv("sharing-dataset-for-analysis.csv")

sc <- read_csv("data/EA-societal-complexity-variables-qc-minerva-sample.csv")


ds <- full_join(ds_FA, sc, by = c("ID", "OWC"))

wf <- read_csv("../minerva/Warfare/Upstream/DT-WarfareViolence-Combined-Clean.csv") %>%
  mutate(
    OWC = str_trim(OWC, side = c("both")),
    State = str_trim(State, side = c("both"))
  )


ds_nostate <- full_join(ds, wf, by = c("ID", "OWC"))

ds_nostate <- ds_nostate %>%
  filter(State == "No")

ggplot(ds_nostate, aes(x = nonfd_2_freq_30 , y = class_strat)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")


```


# hierarchy beyond community

```{r}
ggplot(ds, aes(x = nonfd_2_freq_30 , y = hier_beyond_com)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = nonfd_2.5_freq_30 , y = hier_beyond_com)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = allhazards_nonfd_sev_exposure2_30 , y = hier_beyond_com)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = allhazards_nonfd_sev_exposure2.5_30 , y = hier_beyond_com)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = disaster_nonfd_sev_exposure2_30 , y = hier_beyond_com)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = disaster_nonfd_sev_exposure2.5_30 , y = hier_beyond_com)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = normative_est_count_30.x , y = hier_beyond_com)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

```
```{r}
ggplot(ds, aes(x = nonfd_2_freq_30_IA , y = hier_beyond_com)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = nonfd_2.5_freq_30_IA , y = hier_beyond_com)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = allhazards_nonfd_sev_exposure2_30_IA , y = hier_beyond_com)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = allhazards_nonfd_sev_exposure2.5_30_IA, y = hier_beyond_com)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = disaster_nonfd_sev_exposure2_30_IA , y = hier_beyond_com)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = disaster_nonfd_sev_exposure2.5_30_IA , y = hier_beyond_com)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```


```{r}
ggplot(ds, aes(x = fd_freq_30 , y = hier_beyond_com)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = allhazards_H9a_sev_exposure_30 , y = hier_beyond_com)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = disaster_h9a_sev_exposure_30 , y = hier_beyond_com)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

```


```{r}
ggplot(ds, aes(x = fd_freq_30_IA , y = hier_beyond_com)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = allhazards_H9a_sev_exposure_30_IA, y = hier_beyond_com)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = disaster_h9a_sev_exposure_30_IA, y = hier_beyond_com)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

## Nonfd (Cutoff <2 for food destroying severity)
```{r}
ds$nonfd_2_freq_30_z <- scale(ds$nonfd_2_freq_30)

nonfd_ea033 <- ds[complete.cases(ds[, c("nonfd_2_freq_30_z", "hier_beyond_com")]), ] 


ggplot(nonfd_ea033, aes(x = nonfd_2_freq_30_z , y = hier_beyond_com)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
mod_nonfd_ea033 <- brm(
  formula = hier_beyond_com ~ nonfd_2_freq_30_z,
  data = nonfd_ea033,
  family = cumulative(link = "logit"),  # ordinal outcome
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 1), class = "b"),  # Weakly informative normal priors for the coefficients
    prior(cauchy(0, 1), class = "Intercept")  # Weakly informative Cauchy prior for the intercept
  )
)

summary(mod_nonfd_ea033)
plot(mod_nonfd_ea033, type = "coef")

conditional_effects_plot <- conditional_effects(mod_nonfd_ea033)
plot(conditional_effects_plot)
```

## Nonfd (Cutoff < 2.5 for food destroying severity)
```{r}
ds$nonfd_2.5_freq_30_z <- scale(ds$nonfd_2.5_freq_30)

nonfd_2.5_ea033 <- ds[complete.cases(ds[, c("nonfd_2.5_freq_30_z", "hier_beyond_com")]), ] 

ggplot(nonfd_2.5_ea033, aes(x = nonfd_2.5_freq_30_z , y = hier_beyond_com)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
mod_nonfd_2.5_ea033 <- brm(
  formula = hier_beyond_com ~ nonfd_2.5_freq_30_z,
  data = nonfd_2.5_ea033,
  family = cumulative(link = "logit"),  # ordinal outcome
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 1), class = "b"),  # Weakly informative normal priors for the coefficients
    prior(student_t(3, 0, 2.5), class = "Intercept")  # better than cauchy here
  )
)

summary(mod_nonfd_2.5_ea033)
```

## Food destroying

```{r}
hist(ds$fd_freq_30)

ds$fd_freq_30_z <- scale(ds$fd_freq_30)

fd_ea033 <- ds[complete.cases(ds[, c("fd_freq_30_z", "hier_beyond_com")]), ] 

ggplot(fd_ea033, aes(x = fd_freq_30_z , y = hier_beyond_com)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
mod_fd_ea033 <- brm(
  formula = hier_beyond_com ~ fd_freq_30_z,
  data = fd_ea033,
  family = cumulative(link = "logit"),  # ordinal outcome
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 1), class = "b"),  # Weakly informative normal priors for the coefficients
    prior(student_t(3, 0, 2.5), class = "Intercept")
  )
)

summary(mod_fd_ea033)
```

# Class Strattification 

```{r}
ggplot(ds, aes(x = nonfd_2_freq_30 , y = class_strat)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = nonfd_2.5_freq_30 , y = class_strat)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = allhazards_nonfd_sev_exposure2_30 , y = class_strat)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = allhazards_nonfd_sev_exposure2.5_30 , y = class_strat)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = disaster_nonfd_sev_exposure2_30 , y = class_strat)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = disaster_nonfd_sev_exposure2.5_30 , y = class_strat)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

```

```{r}
ggplot(ds, aes(x = nonfd_2_freq_30_IA , y = class_strat)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = nonfd_2.5_freq_30_IA , y = class_strat)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = allhazards_nonfd_sev_exposure2_30_IA , y = class_strat)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = allhazards_nonfd_sev_exposure2.5_30_IA, y = class_strat)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = disaster_nonfd_sev_exposure2_30_IA , y = class_strat)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = disaster_nonfd_sev_exposure2.5_30_IA , y = class_strat)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
ggplot(ds, aes(x = fd_freq_30 , y = class_strat)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = allhazards_H9a_sev_exposure_30 , y = class_strat)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = disaster_h9a_sev_exposure_30 , y = class_strat)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
ggplot(ds, aes(x = fd_freq_30_IA , y = class_strat)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = allhazards_H9a_sev_exposure_30_IA , y = class_strat)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = disaster_h9a_sev_exposure_30_IA , y = class_strat)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

## Nonfd (Cutoff <2 for food destroying severity)
```{r}
nonfd_class <- ds[complete.cases(ds[, c("nonfd_2_freq_30_z", "class_strat")]), ] 


ggplot(nonfd_class, aes(x = nonfd_2_freq_30_z , y = class_strat)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
mod_nonfd_class <- brm(
  formula = class_strat ~ nonfd_2_freq_30_z,
  data = nonfd_class,
  family = cumulative(link = "logit"),  # ordinal outcome
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 1), class = "b"),  # Weakly informative normal priors for the coefficients
    prior(cauchy(0, 1), class = "Intercept")  # Weakly informative Cauchy prior for the intercept
  )
)

summary(mod_nonfd_class)
```

## Nonfd (Cutoff < 2.5 for food destroying severity)
```{r}
nonfd_2.5_class <- ds[complete.cases(ds[, c("nonfd_2.5_freq_30_z", "class_strat")]), ] 

ggplot(nonfd_2.5_class, aes(x = nonfd_2.5_freq_30_z , y = class_strat)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
mod_nonfd_2.5_class <- brm(
  formula = class_strat ~ nonfd_2.5_freq_30_z,
  data = nonfd_2.5_class,
  family = cumulative(link = "logit"),  # ordinal outcome
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 1), class = "b"),  # Weakly informative normal priors for the coefficients
    prior(student_t(3, 0, 2.5), class = "Intercept")  # better than cauchy here
  )
)

summary(mod_nonfd_2.5_class)
```

## Food destroying

```{r}
fd_class <- ds[complete.cases(ds[, c("fd_freq_30_z", "class_strat")]), ] 

ggplot(fd_class, aes(x = fd_freq_30_z , y = class_strat)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
mod_fd_class <- brm(
  formula = class_strat ~ fd_freq_30_z,
  data = fd_class,
  family = cumulative(link = "logit"),  # ordinal outcome
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 1), class = "b"),  # Weakly informative normal priors for the coefficients
    prior(student_t(3, 0, 2.5), class = "Intercept")
  )
)

summary(mod_fd_class)
```

# community size

```{r}
ggplot(ds, aes(x = nonfd_2_freq_30 , y = community_size)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = nonfd_2.5_freq_30 , y = community_size)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = allhazards_nonfd_sev_exposure2_30 , y = community_size)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = allhazards_nonfd_sev_exposure2.5_30 , y = community_size)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = disaster_nonfd_sev_exposure2_30 , y = community_size)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = disaster_nonfd_sev_exposure2.5_30 , y = community_size)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

```

```{r}
ggplot(ds, aes(x = nonfd_2_freq_30_IA , y = community_size)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = nonfd_2.5_freq_30_IA , y = community_size)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = allhazards_nonfd_sev_exposure2_30_IA , y = community_size)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = allhazards_nonfd_sev_exposure2.5_30_IA , y = community_size)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = disaster_nonfd_sev_exposure2_30_IA , y = community_size)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = disaster_nonfd_sev_exposure2.5_30_IA , y = community_size)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
ggplot(ds, aes(x = fd_freq_30, y = community_size)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = allhazards_H9a_sev_exposure_30, y = community_size)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = disaster_h9a_sev_exposure_30, y = community_size)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
ggplot(ds, aes(x = fd_freq_30_IA , y = community_size)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = allhazards_H9a_sev_exposure_30_IA, y = community_size)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(ds, aes(x = disaster_h9a_sev_exposure_30_IA , y = community_size)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

## Nonfd (Cutoff <2 for food destroying severity)
```{r}
nonfd_size <- ds[complete.cases(ds[, c("nonfd_2_freq_30_z", "community_size")]), ] 


ggplot(nonfd_size, aes(x = nonfd_2_freq_30_z , y = community_size)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
nonfd_size_IA <- ds[complete.cases(ds[, c("nonfd_2_freq_30_IA", "community_size")]), ] 


ggplot(nonfd_size_IA, aes(x = nonfd_2_freq_30_IA , y = community_size)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
mod_nonfd_2_size_IA <- brm(
  formula = community_size ~ nonfd_2_freq_30_IA,
  data = nonfd_size_IA,
  family = cumulative(link = "logit"),  # ordinal outcome
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 1), class = "b"),  # Weakly informative normal priors for the coefficients
    prior(student_t(3, 0, 2.5), class = "Intercept")  # better than cauchy here
  )
)

summary(mod_nonfd_2_size_IA)

hypothesis(mod_nonfd_2_size_IA, "nonfd_2_freq_30_IA > 0")

draws2 <- as_draws_df(mod_nonfd_2_size_IA)

p_nonfd_comsize <- draws2 %>%
  ggplot(aes(x = b_nonfd_2_freq_30_IA)) +
  geom_density(fill = "pink", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(
    title = "Community Size",
    x = expression(beta ~ "(Non-FD Hazard Frequency)"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14)

p_nonfd_comsize
```


## Nonfd (Cutoff < 2.5 for food destroying severity)
```{r}
nonfd_2.5_size <- ds[complete.cases(ds[, c("nonfd_2.5_freq_30_z", "community_size")]), ] 

ggplot(nonfd_2.5_size, aes(x = nonfd_2.5_freq_30_z , y = community_size)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
mod_nonfd_2.5_size <- brm(
  formula = community_size ~ nonfd_2.5_freq_30_z,
  data = nonfd_2.5_size,
  family = cumulative(link = "logit"),  # ordinal outcome
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 1), class = "b"),  # Weakly informative normal priors for the coefficients
    prior(student_t(3, 0, 2.5), class = "Intercept")  # better than cauchy here
  )
)

summary(mod_nonfd_2.5_size)
```

## Food destroying

```{r}
fd_size <- ds[complete.cases(ds[, c("fd_freq_30_z", "community_size")]), ] 

ggplot(fd_size, aes(x = fd_freq_30_z , y = community_size)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
mod_fd_size <- brm(
  formula = community_size ~ fd_freq_30_z,
  data = fd_size,
  family = cumulative(link = "logit"),  # ordinal outcome
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 1), class = "b"),  # Weakly informative normal priors for the coefficients
    prior(student_t(3, 0, 2.5), class = "Intercept")
  )
)

summary(mod_fd_size)
```
