---
title: "`testing-warfare-across-fd-nonfd-hazards"
format: html
editor: visual
---

```{r}
library(tidyverse)
library(brms)

ds_FA <- read_csv("sharing-dataset-for-analysis.csv")

wf <- read_csv("../minerva/Warfare/Upstream/DT-WarfareViolence-Combined-Clean.csv") %>%
  mutate(
    OWC = str_trim(OWC, side = c("both")),
    State = str_trim(State, side = c("both"))
  )

ds <- full_join(ds_FA, wf, by = c("OWC", "ID"))

```

# Variable spreads

```{r}
var_spreads <- ds %>%
  filter(State == "No" & newpac_R < 3)

cor.test(
  var_spreads$ovfreq_R,
  var_spreads$ea033,
  use = "complete.obs",
  method = "spearman"
)


```
## non food destroying vars
```{r}
ggplot(var_spreads, aes(x = ovfreq_R , y = allhazards_nonfd_sev_exposure2.5_30)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

## food destroying vars

```{r}
hist(var_spreads$allhazards_H9a_sev_exposure_30)
hist(var_spreads$allhazards_H9a_sev_exposure_30_IA)
hist(var_spreads$disaster_h9a_sev_exposure_30)
hist(var_spreads$disaster_h9a_sev_exposure_30_IA)
```

```{r}
ggplot(var_spreads, aes(x = ovfreq_R , y = disaster_fd_sev_exposure2.5_30)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(var_spreads, aes(x = ovfreq_R , y = disaster_fd_sev_exposure2.5_30_IA)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(var_spreads, aes(x = ovfreq_R , y = disaster_fd_sev_exposure2_30)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(var_spreads, aes(x = ovfreq_R , y = disaster_fd_sev_exposure2_30_IA)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

```

Distribution for the fd disaster weighted variables appears quite noisy. One important feature however is that points don't begin until level 3 of overall warfare suggesting that even few instances of fd disasters are related to higher warfare frequencies.

```{r}
ggplot(var_spreads, aes(x = ovfreq_R , y = allhazards_H9a_sev_exposure_30 )) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(var_spreads, aes(x = ovfreq_R , y = allhazards_H9a_sev_exposure_30_IA)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(var_spreads, aes(x = ovfreq_R , y = allhazards_fd_sev_exposure2.5_30 )) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(var_spreads, aes(x = ovfreq_R , y = allhazards_fd_sev_exposure2.5_30_IA)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

cor.test(
  var_spreads$allhazards_H9a_sev_exposure_30,
  var_spreads$allhazards_fd_sev_exposure2.5_30,
  use = "complete.obs",
  method = "spearman"
)

```

These two variables appear very similar and are highly correlated. I will use the allhazards_H9a_sev_exposure_30 variable as the food destroying metric.

# Food destroying Hazards

## Overall frequency of warfare

```{r}
fd_ovfreq <- var_spreads[complete.cases(var_spreads[, c("allhazards_fd_sev_exposure2.5_30", "ovfreq_R")]), ] 

fd_ovfreq_cont <- var_spreads[complete.cases(var_spreads[, c("allhazards_fd_sev_exposure2.5_30", "ovfreq_R", "ea033")]), ] 
```



```{r}
mod_fd_ovfreq <- brm(
  formula = ovfreq_R ~ allhazards_fd_sev_exposure2.5_30,
  data = fd_ovfreq,
  family = gaussian(),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),  # Weakly informative normal priors for the coefficients
    prior(cauchy(0, 1), class = "Intercept")  # Weakly informative Cauchy prior for the intercept
  )
)

mod_fd_ovfreq_cont <- brm(
  formula = ovfreq_R ~ allhazards_fd_sev_exposure2.5_30 + mo(ea033),
  data = fd_ovfreq_cont,
  family = gaussian(),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),  # Weakly informative normal priors for the coefficients
    prior(cauchy(0, 1), class = "Intercept")  # Weakly informative Cauchy prior for the intercept
  )
)


summary(mod_fd_ovfreq)
summary(mod_fd_ovfreq_cont)
plot(mod_fd_ovfreq_cont, type = "coef")

conditional_effects_plot <- conditional_effects(mod_fd_ovfreq_cont)
plot(conditional_effects_plot)
```

```{r}
hypothesis(mod_fd_ovfreq, "allhazards_fd_sev_exposure2.5_30 > 0") # they do!

draws2 <- as_draws_df(mod_fd_ovfreq)


x_vals <- draws2$b_allhazards_fd_sev_exposure2.5_30
x_lim <- max(abs(x_vals), na.rm = TRUE)

post_prob <- mean(x_vals > 0, na.rm = TRUE)

pfd_ovfreq <- draws2 %>%
  ggplot(aes(x = b_fd_freq_30_IA)) +
  geom_density(fill = "#ED7D31", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  coord_cartesian(xlim = c(-x_lim, x_lim)) +
  annotate(
    "text",
    x = x_lim * 0.95,
    y = Inf,
    label = paste0("Post. Prob = ", round(post_prob * 100, 1), "%"),
    hjust = 1,
    vjust = 1.5,
    size = 5
  ) +
  labs(
    x = expression(beta ~ "(Food destroying hazards weighted by severity)"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16, margin = margin(b = 10)),
    axis.title = element_text(face = "bold")
  )

pfd_ovfreq_cont
```

```{r}
# in the our better nature paper, daily food sharing was negatively associated with food destroying hazards
hypothesis(mod_fd_ovfreq_cont, "fd_freq_30_IA > 0") # they do!

draws2 <- as_draws_df(mod_fd_ovfreq_cont)


x_vals <- draws2$b_fd_freq_30_IA
x_lim <- max(abs(x_vals), na.rm = TRUE)

post_prob <- mean(x_vals > 0, na.rm = TRUE)

pfd_ovfreq_cont <- draws2 %>%
  ggplot(aes(x = b_fd_freq_30_IA)) +
  geom_density(fill = "#ED7D31", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  coord_cartesian(xlim = c(-x_lim, x_lim)) +
  annotate(
    "text",
    x = x_lim * 0.95,
    y = Inf,
    label = paste0("Post. Prob = ", round(post_prob * 100, 1), "%"),
    hjust = 1,
    vjust = 1.5,
    size = 5
  ) +
  labs(
    x = expression(beta ~ "(Food destroying hazards weighted by severity)"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16, margin = margin(b = 10)),
    axis.title = element_text(face = "bold")
  )

pfd_ovfreq_cont
```

```{r}
fd_ovfreq <- var_spreads[complete.cases(var_spreads[, c("fd_freq_30", "ovfreq_R")]), ] 
```

```{r}
mod_fd_ovfreq <- brm(
  formula = ovfreq_R ~ fd_freq_30,
  data = fd_ovfreq,
  family = gaussian(),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),
    prior(cauchy(0, 1), class = "Intercept")
  )
)

summary(mod_fd_ovfreq)
plot(mod_fd_ovfreq, type = "coef")

conditional_effects_plot <- conditional_effects(mod_fd_ovfreq)
plot(conditional_effects_plot)
```

```{r}
hypothesis(mod_fd_ovfreq, "fd_freq_30 > 0")

draws2 <- as_draws_df(mod_fd_ovfreq)

pfd_ovfreq <- draws2 %>%
  ggplot(aes(x = b_fd_freq_30)) +
  geom_density(fill = "purple", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  labs(
    title = "Overall Warfare Frequency",
    x = expression(beta ~ "(Food Destroying Hazard Frequency)"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16, margin = margin(b = 10)),
    axis.title = element_text(face = "bold")
  )

pfd_ovfreq
```

# Non-Food Destroying Hazards (2.5)

## Overall Warfare

```{r}
nonfd_ovfreq <- var_spreads[
  complete.cases(var_spreads[, c("allhazards_nonfd_sev_exposure2.5_30", "ovfreq_R")]),
]

ggplot(nonfd_ovfreq, aes(x = allhazards_nonfd_sev_exposure2.5_30, y = ovfreq_R)) +
  geom_jitter(width = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
mod_nonfd_ovfreq <- brm(
  formula = ovfreq_R ~ allhazards_nonfd_sev_exposure2.5_30,
  data = nonfd_ovfreq,
  family = gaussian(),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),
    prior(cauchy(0, 1), class = "Intercept")
  )
)

summary(mod_nonfd_ovfreq)
plot(mod_nonfd_ovfreq, type = "coef")

plot(conditional_effects(mod_nonfd_ovfreq))
```

```{r}
hypothesis(mod_nonfd_ovfreq, "allhazards_nonfd_sev_exposure2.5_30 < 0")

draws2 <- as_draws_df(mod_nonfd_ovfreq)

p_nonfd_ovfreq <- draws2 %>%
  ggplot(aes(x = b_allhazards_nonfd_sev_exposure2.5_30)) +
  geom_density(fill = "blue", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(
    title = "Overall Warfare Frequency",
    x = expression(beta ~ "(Non-FD hazard severity weighted by frequency)"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14)

p_nonfd_ovfreq
```

```{r}
nonfd_ovfreq_IA <- var_spreads[
  complete.cases(var_spreads[, c("allhazards_nonfd_sev_exposure2.5_30_IA", "ovfreq_R")]),
]

ggplot(nonfd_ovfreq_IA, aes(x = nonfd_2.5_freq_30_IA, y = ovfreq_R)) +
  geom_jitter(width = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
mod_nonfd_ovfreq_IA <- brm(
  formula = ovfreq_R ~ allhazards_nonfd_sev_exposure2.5_30_IA,
  data = nonfd_ovfreq_IA,
  family = gaussian(),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),
    prior(cauchy(0, 1), class = "Intercept")
  )
)

summary(mod_nonfd_ovfreq_IA)
plot(mod_nonfd_ovfreq_IA, type = "coef")

plot(conditional_effects(mod_nonfd_ovfreq_IA))
```

```{r}
hypothesis(mod_nonfd_ovfreq_IA, "allhazards_nonfd_sev_exposure2.5_30_IA < 0")

draws2 <- as_draws_df(mod_nonfd_ovfreq_IA)

p_nonfd_ovfreq_IA <- draws2 %>%
  ggplot(aes(x = b_allhazards_nonfd_sev_exposure2.5_30_IA)) +
  geom_density(fill = "blue", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(
    title = "Overall Warfare Frequency",
    x = expression(beta ~ "(Non-FD hazard severity weighted by frequency (IA))"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14)

p_nonfd_ovfreq_IA
```


# Non-Food Destroying Hazards (2)

## Overall Warfare

```{r}
nonfd_ovfreq2 <- var_spreads[complete.cases(var_spreads[, c("nonfd_2_freq_30", "ovfreq_R")]),
]


nonfd_ovfreq2_cont <- var_spreads[complete.cases(var_spreads[, c("nonfd_2_freq_30", "ovfreq_R", "ea033")]),
]

ggplot(nonfd_ovfreq2, aes(x = nonfd_2_freq_30, y = ovfreq_R)) +
  geom_jitter(width = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
mod_nonfd_ovfreq2 <- brm(
  formula = ovfreq_R ~ nonfd_2_freq_30,
  data = nonfd_ovfreq2,
  family = gaussian(),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),
    prior(cauchy(0, 1), class = "Intercept")
  )
)

mod_nonfd_ovfreq2_cont <- brm(
  formula = ovfreq_R ~ nonfd_2_freq_30 + mo(ea033),
  data = nonfd_ovfreq2,
  family = gaussian(),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),
    prior(cauchy(0, 1), class = "Intercept")
  )
)

summary(mod_nonfd_ovfreq2)
summary(mod_nonfd_ovfreq2_cont)

plot(mod_nonfd_ovfreq2, type = "coef")

plot(conditional_effects(mod_nonfd_ovfreq2))
```

```{r}
hypothesis(mod_nonfd_ovfreq2, "nonfd_2_freq_30 < 0")

draws2 <- as_draws_df(mod_nonfd_ovfreq2)

p_nonfd_ovfreq2 <- draws2 %>%
  ggplot(aes(x = b_nonfd_2_freq_30)) +
  geom_density(fill = "blue", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(
    title = "Overall Warfare Frequency",
    x = expression(beta ~ "(Non-FD Hazard Frequency (FD < 2))"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14)

p_nonfd_ovfreq2
```

```{r}
draws2 <- as_draws_df(mod_nonfd_ovfreq2)


x_vals <- draws2$b_nonfd_2_freq_30
x_lim <- max(abs(x_vals), na.rm = TRUE)

post_prob <- mean(x_vals > 0, na.rm = TRUE)

pnfd_ovfreq <- draws2 %>%
  ggplot(aes(x = b_nonfd_2_freq_30)) +
  geom_density(fill = "#0070C0", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  coord_cartesian(xlim = c(-x_lim, x_lim)) +
  annotate(
    "text",
    x = x_lim * 0.95,
    y = Inf,
    label = paste0("Post. Prob = ", round(post_prob * 100, 1), "%"),
    hjust = 1,
    vjust = 1.5,
    size = 5
  ) +
  labs(
    x = expression(beta ~ "(Food destroying hazards weighted by severity)"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16, margin = margin(b = 10)),
    axis.title = element_text(face = "bold")
  )

pnfd_ovfreq
```

```{r}
nonfd_ovfreq2_IA <- var_spreads[
  complete.cases(var_spreads[, c("nonfd_2_freq_30_IA", "ovfreq_R")]),
]

nonfd_ovfreq2_IA_cont <- var_spreads[
  complete.cases(var_spreads[, c("nonfd_2_freq_30_IA", "ovfreq_R","ea033")]),
]

ggplot(nonfd_ovfreq2_IA, aes(x = nonfd_2_freq_30_IA, y = ovfreq_R)) +
  geom_jitter(width = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
mod_nonfd_ovfreq2_IA <- brm(
  formula = ovfreq_R ~ nonfd_2_freq_30_IA,
  data = nonfd_ovfreq2_IA,
  family = gaussian(),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),
    prior(cauchy(0, 1), class = "Intercept")
  )
)

mod_nonfd_ovfreq2_IA_cont <- brm(
  formula = ovfreq_R ~ nonfd_2_freq_30_IA + mo(ea033),
  data = nonfd_ovfreq2_IA,
  family = gaussian(),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),
    prior(cauchy(0, 1), class = "Intercept")
  )
)

summary(mod_nonfd_ovfreq2_IA)
summary(mod_nonfd_ovfreq2_IA_cont)

plot(mod_nonfd_ovfreq2_IA, type = "coef")

plot(conditional_effects(mod_nonfd_ovfreq2_IA))
```

```{r}
hypothesis(mod_nonfd_ovfreq2_IA, "nonfd_2_freq_30_IA < 0")

draws2 <- as_draws_df(mod_nonfd_ovfreq2_IA)

p_nonfd_ovfreq2_IA <- draws2 %>%
  ggplot(aes(x = b_nonfd_2_freq_30_IA)) +
  geom_density(fill = "blue", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(
    title = "Overall Warfare Frequency",
    x = expression(beta ~ "(Non-FD Hazard Frequency (IA; FD < 2))"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14)

p_nonfd_ovfreq2_IA
```

```{r}
draws2 <- as_draws_df(mod_nonfd_ovfreq2_IA)


x_vals <- draws2$b_nonfd_2_freq_30_IA
x_lim <- max(abs(x_vals), na.rm = TRUE)

post_prob <- mean(x_vals < 0, na.rm = TRUE)

pnfd_ovfreq_IA <- draws2 %>%
  ggplot(aes(x = b_nonfd_2_freq_30_IA)) +
  geom_density(fill = "#0070C0", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  coord_cartesian(xlim = c(-x_lim, x_lim)) +
  annotate(
    "text",
    x = x_lim * 0.95,
    y = Inf,
    label = paste0("Post. Prob = ", round(post_prob * 100, 1), "%"),
    hjust = 1,
    vjust = 1.5,
    size = 5
  ) +
  labs(
    x = expression(beta ~ "(Non-food destroying hazards weighted by severity)"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16, margin = margin(b = 10)),
    axis.title = element_text(face = "bold")
  )

pnfd_ovfreq_IA
```

```{r}
draws2 <- as_draws_df(mod_nonfd_ovfreq2_IA_cont)


x_vals <- draws2$b_nonfd_2_freq_30_IA
x_lim <- max(abs(x_vals), na.rm = TRUE)

post_prob <- mean(x_vals < 0, na.rm = TRUE)

pnfd_ovfreq_IA_cont <- draws2 %>%
  ggplot(aes(x = b_nonfd_2_freq_30_IA)) +
  geom_density(fill = "#0070C0", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  coord_cartesian(xlim = c(-x_lim, x_lim)) +
  annotate(
    "text",
    x = x_lim * 0.95,
    y = Inf,
    label = paste0("Post. Prob = ", round(post_prob * 100, 1), "%"),
    hjust = 1,
    vjust = 1.5,
    size = 5
  ) +
  labs(
    x = expression(beta ~ "(Non-food destroying hazards weighted by severity)"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16, margin = margin(b = 10)),
    axis.title = element_text(face = "bold")
  )

pnfd_ovfreq_IA_cont
```

