---
title: "`testing-warfare-across-fd-nonfd-hazards"
format: html
editor: visual
---

```{r}
library(tidyverse)
library(brms)

ds_FA <- read_csv("sharing-dataset-for-analysis.csv")

wf <- read_csv("../minerva/Warfare/Upstream/DT-WarfareViolence-Combined-Clean.csv") %>%
  mutate(
    OWC = str_trim(OWC, side = c("both")),
    State = str_trim(State, side = c("both"))
  )

ds <- full_join(ds_FA, wf, by = c("OWC", "ID"))

```
# Variable spreads
```{r}
var_spreads <- ds %>%
  filter(State == "No" & newpac_R < 3)
```

## food destroying vars

```{r}
hist(var_spreads$allhazards_H9a_sev_exposure_30)
hist(var_spreads$allhazards_H9a_sev_exposure_30_IA)
hist(var_spreads$disaster_h9a_sev_exposure_30)
hist(var_spreads$disaster_h9a_sev_exposure_30_IA)
hist(var_spreads$fd_freq_30)
hist(var_spreads$fd_freq_30_IA)
```

```{r}
ggplot(var_spreads, aes(x = ovfreq_R , y = allhazards_H9a_sev_exposure_30 )) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(var_spreads, aes(x = ovfreq_R , y = allhazards_H9a_sev_exposure_30_IA )) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(var_spreads, aes(x = ovfreq_R , y = disaster_h9a_sev_exposure_30 )) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(var_spreads, aes(x = ovfreq_R , y = disaster_h9a_sev_exposure_30_IA )) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(var_spreads, aes(x = ovfreq_R , y = fd_freq_30 )) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(var_spreads, aes(x = ovfreq_R , y = fd_freq_30_IA)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

# Food destroying Hazards

## Overall frequency of warfare
```{r}
fd_ovfreq_IA <- var_spreads[complete.cases(var_spreads[, c("fd_freq_30_IA", "ovfreq_R")]), ] 
```

```{r}
ggplot(fd_ovfreq_IA, aes(x = ovfreq_R , y = fd_freq_30_IA)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

# sensitivity analysis
# fd_ovfreq$z_sev <- scale(fd_ovfreq$fd_freq_30_IA)

# fd_ovfreq_trim <- fd_ovfreq[abs(fd_ovfreq$z_sev) <= 2, ]


# ggplot(fd_ovfreq_trim, aes(x = ovfreq_R, y = fd_freq_30_IA)) +
#   geom_jitter(height = 0.05, alpha = 0.6) +
#   geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")


test <- lm(ovfreq_R ~ fd_freq_30_IA, data = fd_ovfreq_IA)
summary(test)
plot(test)


test_no26 <- lm(ovfreq_R ~ fd_freq_30_IA,
                data = fd_ovfreq_IA[-26, ])

summary(test)
summary(test_no26)
```

```{r}
mod_fd_ovfreq_IA <- brm(
  formula = ovfreq_R ~ fd_freq_30_IA,
  data = fd_ovfreq,
  family = gaussian(),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),  # Weakly informative normal priors for the coefficients
    prior(cauchy(0, 1), class = "Intercept")  # Weakly informative Cauchy prior for the intercept
  )
)

summary(mod_fd_ovfreq_IA)
plot(mod_fd_ovfreq_IA, type = "coef")

conditional_effects_plot <- conditional_effects(mod_fd_ovfreq_IA)
plot(conditional_effects_plot)
```

```{r}
# in the our better nature paper, daily food sharing was negatively associated with food destroying hazards
hypothesis(mod_fd_ovfreq_IA, "fd_freq_30_IA > 0") # they do!

draws2 <- as_draws_df(mod_fd_ovfreq_IA)

# Plot for Sev
pfd_ovfreq_IA <- draws2 %>%
  ggplot(aes(x = b_fd_freq_30_IA)) +
  geom_density(fill = "purple", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  labs(
    title = "Overall Warfare Frequency",
    x = expression(beta ~ "(Food Destroying Hazard Frequency (IA))"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16, margin = margin(b = 10)),
    axis.title = element_text(face = "bold")
  )

pfd_ovfreq_IA
```

```{r}
fd_ovfreq <- var_spreads[complete.cases(var_spreads[, c("fd_freq_30", "ovfreq_R")]), ] 
```

```{r}
mod_fd_ovfreq <- brm(
  formula = ovfreq_R ~ fd_freq_30,
  data = fd_ovfreq,
  family = gaussian(),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),
    prior(cauchy(0, 1), class = "Intercept")
  )
)

summary(mod_fd_ovfreq)
plot(mod_fd_ovfreq, type = "coef")

conditional_effects_plot <- conditional_effects(mod_fd_ovfreq)
plot(conditional_effects_plot)
```

```{r}
hypothesis(mod_fd_ovfreq, "fd_freq_30 > 0")

draws2 <- as_draws_df(mod_fd_ovfreq)

pfd_ovfreq <- draws2 %>%
  ggplot(aes(x = b_fd_freq_30)) +
  geom_density(fill = "purple", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  labs(
    title = "Overall Warfare Frequency",
    x = expression(beta ~ "(Food Destroying Hazard Frequency)"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16, margin = margin(b = 10)),
    axis.title = element_text(face = "bold")
  )

pfd_ovfreq
```

## External Warfare 
```{r}
fd_extfreq <- var_spreads[complete.cases(var_spreads[, c("fd_freq_30", "extfreq_R")]), ] 
```

```{r}
ggplot(fd_extfreq, aes(x = fd_freq_30, y = extfreq_R)) +
  geom_jitter(width = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

# sensitivity analysis
# fd_extfreq$z_sev <- scale(fd_extfreq$fd_freq_30)

# fd_extfreq_trim <- fd_extfreq[abs(fd_extfreq$z_sev) <= 2, ]

# ggplot(fd_extfreq_trim, aes(x = fd_freq_30, y = extfreq_R)) +
#   geom_jitter(width = 0.05, alpha = 0.6) +
#   geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```
```{r}
test <- lm(extfreq_R ~ fd_freq_30, data = fd_extfreq)
summary(test)
plot(test)

test_no17 <- lm(extfreq_R ~ fd_freq_30,
                data = fd_extfreq[-17, ])

summary(test_full)
summary(test_no26)
```

```{r}
mod_fd_extfreq <- brm(
  formula = extfreq_R ~ fd_freq_30,
  data = fd_extfreq,
  family = gaussian(),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),
    prior(cauchy(0, 1), class = "Intercept")
  )
)

summary(mod_fd_extfreq)
plot(mod_fd_extfreq, type = "coef")

conditional_effects_plot <- conditional_effects(mod_fd_extfreq)
plot(conditional_effects_plot)
```

```{r}
hypothesis(mod_fd_extfreq, "fd_freq_30 > 0")

draws2 <- as_draws_df(mod_fd_extfreq)

pfd_extfreq <- draws2 %>%
  ggplot(aes(x = b_fd_freq_30)) +
  geom_density(fill = "purple", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  labs(
    title = "External Warfare Frequency",
    x = expression(beta ~ "(Food Destroying Hazard Frequency)"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16, margin = margin(b = 10)),
    axis.title = element_text(face = "bold")
  )

pfd_extfreq
```


```{r}
fd_extfreq_IA <- var_spreads[complete.cases(var_spreads[, c("fd_freq_30_IA", "extfreq_R")]), ] 
```


```{r}
ggplot(fd_extfreq_IA, aes(x = fd_freq_30_IA, y = extfreq_R)) +
  geom_jitter(width = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```
```{r}
test <- lm(extfreq_R ~ fd_freq_30_IA, data = fd_extfreq_IA)
summary(test)
plot(test)

test_no27 <- lm(extfreq_R ~ fd_freq_30_IA,
                data = fd_extfreq_IA[-27, ])

summary(test_no27)
```

```{r}
mod_fd_extfreq_IA <- brm(
  formula = extfreq_R ~ fd_freq_30_IA,
  data = fd_extfreq_IA,
  family = gaussian(),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),
    prior(cauchy(0, 1), class = "Intercept")
  )
)

summary(mod_fd_extfreq_IA)
plot(mod_fd_extfreq_IA, type = "coef")

conditional_effects_plot <- conditional_effects(mod_fd_extfreq_IA)
plot(conditional_effects_plot)
```

```{r}
hypothesis(mod_fd_extfreq_IA, "fd_freq_30_IA > 0")

draws2 <- as_draws_df(mod_fd_extfreq_IA)

pfd_extfreq_IA <- draws2 %>%
  ggplot(aes(x = b_fd_freq_30_IA)) +
  geom_density(fill = "purple", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  labs(
    title = "External Warfare Frequency",
    x = expression(beta ~ "(Food Destroying Hazard Frequency (IA))"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16, margin = margin(b = 10)),
    axis.title = element_text(face = "bold")
  )

pfd_extfreq_IA
```
## Internal Warfare

```{r}
fd_intrfreq <- var_spreads[complete.cases(var_spreads[, c("fd_freq_30", "intrfreq_R")]), ] 

ggplot(fd_intrfreq, aes(x = fd_freq_30, y = intrfreq_R)) +
  geom_jitter(width = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
mod_fd_intrfreq <- brm(
  formula = intrfreq_R ~ fd_freq_30,
  data = fd_intrfreq,
  family = gaussian(),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),
    prior(cauchy(0, 1), class = "Intercept")
  )
)

summary(mod_fd_intrfreq)
plot(mod_fd_intrfreq, type = "coef")

conditional_effects_plot <- conditional_effects(mod_fd_intrfreq)
plot(conditional_effects_plot)
```

```{r}
hypothesis(mod_fd_intrfreq, "fd_freq_30 > 0")

draws2 <- as_draws_df(mod_fd_intrfreq)

pfd_intrfreq <- draws2 %>%
  ggplot(aes(x = b_fd_freq_30)) +
  geom_density(fill = "purple", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  labs(
    title = "Internal Warfare Frequency",
    x = expression(beta ~ "(Food Destroying Hazard Frequency)"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16, margin = margin(b = 10)),
    axis.title = element_text(face = "bold")
  )

pfd_intrfreq
```


```{r}
fd_intrfreq_IA <- var_spreads[complete.cases(var_spreads[, c("fd_freq_30_IA", "intrfreq_R")]), ] 


ggplot(fd_intrfreq_IA, aes(x = fd_freq_30_IA, y = intrfreq_R)) +
  geom_jitter(width = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```
```{r}
mod_fd_intrfreq_IA <- brm(
  formula = intrfreq_R ~ fd_freq_30_IA,
  data = fd_intrfreq_IA,
  family = gaussian(),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),
    prior(cauchy(0, 1), class = "Intercept")
  )
)

summary(mod_fd_intrfreq_IA)
plot(mod_fd_intrfreq_IA, type = "coef")

conditional_effects_plot <- conditional_effects(mod_fd_intrfreq_IA)
plot(conditional_effects_plot)
```


```{r}
hypothesis(mod_fd_intrfreq_IA, "fd_freq_30_IA > 0")

draws2 <- as_draws_df(mod_fd_intrfreq_IA)

pfd_intrfreq_IA <- draws2 %>%
  ggplot(aes(x = b_fd_freq_30_IA)) +
  geom_density(fill = "purple", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  labs(
    title = "Internal Warfare Frequency",
    x = expression(beta ~ "(Food Destroying Hazard Frequency (IA))"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16, margin = margin(b = 10)),
    axis.title = element_text(face = "bold")
  )

pfd_intrfreq_IA
```



# Non-Food Destroying Hazards (2.5)
## Overall Warfare
```{r}
nonfd_ovfreq <- var_spreads[
  complete.cases(var_spreads[, c("nonfd_2.5_freq_30", "ovfreq_R")]),
]

ggplot(nonfd_ovfreq, aes(x = nonfd_2.5_freq_30, y = ovfreq_R)) +
  geom_jitter(width = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
mod_nonfd_ovfreq <- brm(
  formula = ovfreq_R ~ nonfd_2.5_freq_30,
  data = nonfd_ovfreq,
  family = gaussian(),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),
    prior(cauchy(0, 1), class = "Intercept")
  )
)

summary(mod_nonfd_ovfreq)
plot(mod_nonfd_ovfreq, type = "coef")

plot(conditional_effects(mod_nonfd_ovfreq))
```

```{r}
hypothesis(mod_nonfd_ovfreq, "nonfd_2.5_freq_30 < 0")

draws2 <- as_draws_df(mod_nonfd_ovfreq)

p_nonfd_ovfreq <- draws2 %>%
  ggplot(aes(x = b_nonfd_2.5_freq_30)) +
  geom_density(fill = "blue", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(
    title = "Overall Warfare Frequency",
    x = expression(beta ~ "(Non-FD Hazard Frequency)"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14)

p_nonfd_ovfreq
```

```{r}
nonfd_ovfreq_IA <- var_spreads[
  complete.cases(var_spreads[, c("nonfd_2.5_freq_30_IA", "ovfreq_R")]),
]

ggplot(nonfd_ovfreq_IA, aes(x = nonfd_2.5_freq_30_IA, y = ovfreq_R)) +
  geom_jitter(width = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
mod_nonfd_ovfreq_IA <- brm(
  formula = ovfreq_R ~ nonfd_2.5_freq_30_IA,
  data = nonfd_ovfreq_IA,
  family = gaussian(),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),
    prior(cauchy(0, 1), class = "Intercept")
  )
)

summary(mod_nonfd_ovfreq_IA)
plot(mod_nonfd_ovfreq_IA, type = "coef")

plot(conditional_effects(mod_nonfd_ovfreq_IA))
```

```{r}
hypothesis(mod_nonfd_ovfreq_IA, "nonfd_2.5_freq_30_IA < 0")

draws2 <- as_draws_df(mod_nonfd_ovfreq_IA)

p_nonfd_ovfreq_IA <- draws2 %>%
  ggplot(aes(x = b_nonfd_2.5_freq_30_IA)) +
  geom_density(fill = "blue", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(
    title = "Overall Warfare Frequency",
    x = expression(beta ~ "(Non-FD Hazard Frequency (IA))"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14)

p_nonfd_ovfreq_IA
```

## External Warfare
```{r}
nonfd_extfreq <- var_spreads[
  complete.cases(var_spreads[, c("nonfd_2.5_freq_30", "extfreq_R")]),
]

ggplot(nonfd_extfreq, aes(x = nonfd_2.5_freq_30, y = extfreq_R)) +
  geom_jitter(width = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
mod_nonfd_extfreq <- brm(
  formula = extfreq_R ~ nonfd_2.5_freq_30,
  data = nonfd_extfreq,
  family = gaussian(),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),
    prior(cauchy(0, 1), class = "Intercept")
  )
)

summary(mod_nonfd_extfreq)
plot(mod_nonfd_extfreq, type = "coef")

plot(conditional_effects(mod_nonfd_extfreq))
```

```{r}
hypothesis(mod_nonfd_extfreq, "nonfd_2.5_freq_30 < 0")

draws2 <- as_draws_df(mod_nonfd_extfreq)

p_nonfd_extfreq <- draws2 %>%
  ggplot(aes(x = b_nonfd_2.5_freq_30)) +
  geom_density(fill = "blue", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(
    title = "External Warfare Frequency",
    x = expression(beta ~ "(Non-FD Hazard Frequency)"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14)

p_nonfd_extfreq
```


```{r}
nonfd_extfreq_IA <- var_spreads[
  complete.cases(var_spreads[, c("nonfd_2.5_freq_30_IA", "extfreq_R")]),
]

ggplot(nonfd_extfreq_IA, aes(x = nonfd_2.5_freq_30_IA, y = extfreq_R)) +
  geom_jitter(width = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
mod_nonfd_extfreq_IA <- brm(
  formula = extfreq_R ~ nonfd_2.5_freq_30_IA,
  data = nonfd_extfreq_IA,
  family = gaussian(),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),
    prior(cauchy(0, 1), class = "Intercept")
  )
)

summary(mod_nonfd_extfreq_IA)
plot(mod_nonfd_extfreq_IA, type = "coef")

plot(conditional_effects(mod_nonfd_extfreq_IA))
```

```{r}
hypothesis(mod_nonfd_extfreq_IA, "nonfd_2.5_freq_30_IA < 0")

draws2 <- as_draws_df(mod_nonfd_extfreq_IA)

p_nonfd_extfreq_IA <- draws2 %>%
  ggplot(aes(x = b_nonfd_2.5_freq_30_IA)) +
  geom_density(fill = "blue", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(
    title = "External Warfare Frequency",
    x = expression(beta ~ "(Non-FD Hazard Frequency (IA))"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14)

p_nonfd_extfreq_IA
```

## Internal Warfare
```{r}
nonfd_intrfreq <- var_spreads[
  complete.cases(var_spreads[, c("nonfd_2.5_freq_30", "intrfreq_R")]),
]

ggplot(nonfd_intrfreq, aes(x = nonfd_2.5_freq_30, y = intrfreq_R)) +
  geom_jitter(width = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
mod_nonfd_intrfreq <- brm(
  formula = intrfreq_R ~ nonfd_2.5_freq_30,
  data = nonfd_intrfreq,
  family = gaussian(),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),
    prior(cauchy(0, 1), class = "Intercept")
  )
)

summary(mod_nonfd_intrfreq)
plot(mod_nonfd_intrfreq, type = "coef")

plot(conditional_effects(mod_nonfd_intrfreq))
```

```{r}
hypothesis(mod_nonfd_intrfreq, "nonfd_2.5_freq_30 < 0")

draws2 <- as_draws_df(mod_nonfd_intrfreq)

p_nonfd_intrfreq <- draws2 %>%
  ggplot(aes(x = b_nonfd_2.5_freq_30)) +
  geom_density(fill = "blue", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(
    title = "Internal Warfare Frequency",
    x = expression(beta ~ "(Non-FD Hazard Frequency)"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14)

p_nonfd_intrfreq
```

```{r}
nonfd_intrfreq_IA <- var_spreads[
  complete.cases(var_spreads[, c("nonfd_2.5_freq_30_IA", "intrfreq_R")]),
]

ggplot(nonfd_intrfreq_IA, aes(x = nonfd_2.5_freq_30_IA, y = intrfreq_R)) +
  geom_jitter(width = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
mod_nonfd_intrfreq_IA <- brm(
  formula = intrfreq_R ~ nonfd_2.5_freq_30_IA,
  data = nonfd_intrfreq_IA,
  family = gaussian(),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),
    prior(cauchy(0, 1), class = "Intercept")
  )
)

summary(mod_nonfd_intrfreq_IA)
plot(mod_nonfd_intrfreq_IA, type = "coef")

plot(conditional_effects(mod_nonfd_intrfreq_IA))
```

```{r}
hypothesis(mod_nonfd_intrfreq_IA, "nonfd_2.5_freq_30_IA < 0")

draws2 <- as_draws_df(mod_nonfd_intrfreq_IA)

p_nonfd_intrfreq_IA <- draws2 %>%
  ggplot(aes(x = b_nonfd_2.5_freq_30_IA)) +
  geom_density(fill = "blue", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(
    title = "Internal Warfare Frequency",
    x = expression(beta ~ "(Non-FD Hazard Frequency (IA))"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14)

p_nonfd_intrfreq_IA
```


# Non-Food Destroying Hazards (2)
## Overall Warfare
```{r}
nonfd_ovfreq2 <- var_spreads[
  complete.cases(var_spreads[, c("nonfd_2_freq_30", "ovfreq_R")]),
]

ggplot(nonfd_ovfreq2, aes(x = nonfd_2_freq_30, y = ovfreq_R)) +
  geom_jitter(width = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
mod_nonfd_ovfreq2 <- brm(
  formula = ovfreq_R ~ nonfd_2_freq_30,
  data = nonfd_ovfreq2,
  family = gaussian(),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),
    prior(cauchy(0, 1), class = "Intercept")
  )
)

summary(mod_nonfd_ovfreq2)
plot(mod_nonfd_ovfreq2, type = "coef")

plot(conditional_effects(mod_nonfd_ovfreq2))
```

```{r}
hypothesis(mod_nonfd_ovfreq2, "nonfd_2_freq_30 < 0")

draws2 <- as_draws_df(mod_nonfd_ovfreq2)

p_nonfd_ovfreq2 <- draws2 %>%
  ggplot(aes(x = b_nonfd_2_freq_30)) +
  geom_density(fill = "blue", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(
    title = "Overall Warfare Frequency",
    x = expression(beta ~ "(Non-FD Hazard Frequency (FD < 2))"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14)

p_nonfd_ovfreq2
```

```{r}
nonfd_ovfreq2_IA <- var_spreads[
  complete.cases(var_spreads[, c("nonfd_2_freq_30_IA", "ovfreq_R")]),
]

ggplot(nonfd_ovfreq2_IA, aes(x = nonfd_2_freq_30_IA, y = ovfreq_R)) +
  geom_jitter(width = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
mod_nonfd_ovfreq2_IA <- brm(
  formula = ovfreq_R ~ nonfd_2_freq_30_IA,
  data = nonfd_ovfreq2_IA,
  family = gaussian(),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),
    prior(cauchy(0, 1), class = "Intercept")
  )
)

summary(mod_nonfd_ovfreq2_IA)
plot(mod_nonfd_ovfreq2_IA, type = "coef")

plot(conditional_effects(mod_nonfd_ovfreq2_IA))
```

```{r}
hypothesis(mod_nonfd_ovfreq2_IA, "nonfd_2_freq_30_IA < 0")

draws2 <- as_draws_df(mod_nonfd_ovfreq2_IA)

p_nonfd_ovfreq2_IA <- draws2 %>%
  ggplot(aes(x = b_nonfd_2_freq_30_IA)) +
  geom_density(fill = "blue", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(
    title = "Overall Warfare Frequency",
    x = expression(beta ~ "(Non-FD Hazard Frequency (IA; FD < 2))"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14)

p_nonfd_ovfreq2_IA
```

## External Warfare
```{r}
nonfd_extfreq2 <- var_spreads[
  complete.cases(var_spreads[, c("nonfd_2_freq_30", "extfreq_R")]),
]

ggplot(nonfd_extfreq2, aes(x = nonfd_2_freq_30, y = extfreq_R)) +
  geom_jitter(width = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
mod_nonfd_extfreq2 <- brm(
  formula = extfreq_R ~ nonfd_2_freq_30,
  data = nonfd_extfreq2,
  family = gaussian(),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),
    prior(cauchy(0, 1), class = "Intercept")
  )
)

summary(mod_nonfd_extfreq2)
plot(mod_nonfd_extfreq2, type = "coef")

plot(conditional_effects(mod_nonfd_extfreq2))
```

```{r}
hypothesis(mod_nonfd_extfreq2, "nonfd_2_freq_30 < 0")

draws2 <- as_draws_df(mod_nonfd_extfreq2)

p_nonfd_extfreq2 <- draws2 %>%
  ggplot(aes(x = b_nonfd_2_freq_30)) +
  geom_density(fill = "blue", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(
    title = "External Warfare Frequency",
    x = expression(beta ~ "(Non-FD Hazard Frequency (FD < 2))"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14)

p_nonfd_extfreq2
```


```{r}
nonfd_extfreq2_IA <- var_spreads[
  complete.cases(var_spreads[, c("nonfd_2_freq_30_IA", "extfreq_R")]),
]

ggplot(nonfd_extfreq2_IA, aes(x = nonfd_2_freq_30_IA, y = extfreq_R)) +
  geom_jitter(width = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
mod_nonfd_extfreq2_IA <- brm(
  formula = extfreq_R ~ nonfd_2_freq_30_IA,
  data = nonfd_extfreq2_IA,
  family = gaussian(),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),
    prior(cauchy(0, 1), class = "Intercept")
  )
)

summary(mod_nonfd_extfreq2_IA)
plot(mod_nonfd_extfreq2_IA, type = "coef")

plot(conditional_effects(mod_nonfd_extfreq2_IA))
```

```{r}
hypothesis(mod_nonfd_extfreq2_IA, "nonfd_2_freq_30_IA < 0")

draws2 <- as_draws_df(mod_nonfd_extfreq2_IA)

p_nonfd_extfreq2_IA <- draws2 %>%
  ggplot(aes(x = b_nonfd_2_freq_30_IA)) +
  geom_density(fill = "blue", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(
    title = "External Warfare Frequency",
    x = expression(beta ~ "(Non-FD Hazard Frequency (IA; FD < 2))"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14)

p_nonfd_extfreq_IA
```

## Internal Warfare
```{r}
nonfd_intrfreq2 <- var_spreads[
  complete.cases(var_spreads[, c("nonfd_2_freq_30", "intrfreq_R")]),
]

ggplot(nonfd_intrfreq2, aes(x = nonfd_2_freq_30, y = intrfreq_R)) +
  geom_jitter(width = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
mod_nonfd_intrfreq2 <- brm(
  formula = intrfreq_R ~ nonfd_2_freq_30,
  data = nonfd_intrfreq2,
  family = gaussian(),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),
    prior(cauchy(0, 1), class = "Intercept")
  )
)

summary(mod_nonfd_intrfreq2)
plot(mod_nonfd_intrfreq2, type = "coef")

plot(conditional_effects(mod_nonfd_intrfreq2))
```

```{r}
hypothesis(mod_nonfd_intrfreq2, "nonfd_2_freq_30 < 0")

draws2 <- as_draws_df(mod_nonfd_intrfreq2)

p_nonfd_intrfreq2 <- draws2 %>%
  ggplot(aes(x = b_nonfd_2_freq_30)) +
  geom_density(fill = "blue", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(
    title = "Internal Warfare Frequency",
    x = expression(beta ~ "(Non-FD Hazard Frequency (FD < 2) )"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14)

p_nonfd_intrfreq2
```

```{r}
nonfd_intrfreq2_IA <- var_spreads[
  complete.cases(var_spreads[, c("nonfd_2_freq_30_IA", "intrfreq_R")]),
]

ggplot(nonfd_intrfreq2_IA, aes(x = nonfd_2_freq_30_IA, y = intrfreq_R)) +
  geom_jitter(width = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
mod_nonfd_intrfreq2_IA <- brm(
  formula = intrfreq_R ~ nonfd_2_freq_30_IA,
  data = nonfd_intrfreq2_IA,
  family = gaussian(),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),
    prior(cauchy(0, 1), class = "Intercept")
  )
)

summary(mod_nonfd_intrfreq2_IA)
plot(mod_nonfd_intrfreq2_IA, type = "coef")

plot(conditional_effects(mod_nonfd_intrfreq2_IA))
```

```{r}
hypothesis(mod_nonfd_intrfreq2_IA, "nonfd_2_freq_30_IA < 0")

draws2 <- as_draws_df(mod_nonfd_intrfreq2_IA)

p_nonfd_intrfreq2_IA <- draws2 %>%
  ggplot(aes(x = b_nonfd_2_freq_30_IA)) +
  geom_density(fill = "blue", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  labs(
    title = "Internal Warfare Frequency",
    x = expression(beta ~ "(Non-FD Hazard Frequency (IA; FD < 2))"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14)

p_nonfd_intrfreq2_IA
```



# OUTDATED

```{r}
ggplot(var_spreads, aes(x = ovfreq_R , y = allhazards_ )) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

```

```{r}
nonfd_ovfreq <- ds[complete.cases(ds[, c("allhazards_", "ovfreq_R")]), ] 

nonfd_ovfreq <- nonfd_ovfreq %>%
  filter(State == "No" & newpac_R < 3)
```

```{r}
ggplot(nonfd_ovfreq, aes(x = ovfreq_R, y = nonfd_2_freq_30)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

# sensitivity analysis
nonfd_ovfreq$z_sev <- scale(nonfd_ovfreq$nonfd_2_freq_30)

nonfd_ovfreq_trim <- nonfd_ovfreq[abs(nonfd_ovfreq$z_sev) <= 2, ]


ggplot(nonfd_ovfreq_trim, aes(x = ovfreq_R, y = nonfd_2_freq_30)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
mod_fd_ovfreq <- brm(
  formula = ovfreq_R ~ fd_freq_30_IA,
  data = fd_ovfreq,
  family = gaussian(),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),  # Weakly informative normal priors for the coefficients
    prior(cauchy(0, 1), class = "Intercept")  # Weakly informative Cauchy prior for the intercept
  )
)

summary(mod_fd_ovfreq)
plot(mod_fd_ovfreq, type = "coef")

conditional_effects_plot <- conditional_effects(mod_fd_ovfreq)
plot(conditional_effects_plot)
```

```{r}
# in the our better nature paper, daily food sharing was negatively associated with food destroying hazards
hypothesis(mod_fd_ovfreq, "fd_freq_30_IA > 0") # they do!

draws2 <- as_draws_df(mod_fd_ovfreq)

# Plot for Sev
pfd_ovfreq <- draws2 %>%
  ggplot(aes(x = b_fd_freq_30_IA)) +
  geom_density(fill = "purple", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  labs(
    title = "Overall Warfare Frequency",
    x = expression(beta ~ "(Food Destroying Hazard Frequency)"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16, margin = margin(b = 10)),
    axis.title = element_text(face = "bold")
  )

pfd_ovfreq
```

## extfreq_R

```{r}
fd_extfreq <- ds[complete.cases(ds[, c("disaster_h9a_sev_exposure_30_IA", "extfreq_R")]), ]

fd_extfreq <- fd_extfreq %>%
  mutate(
    extfreq_rebin = case_when(
      extfreq_R < 2 ~ "Rare",
      extfreq_R < 4 ~ "Occasional",
      TRUE          ~ "Frequent"
    ),
    extfreq_rebin_large = case_when(
      extfreq_R < 1.75 ~ "Rare/Absent",
      extfreq_R < 2.75 ~ "Low (3–10 yrs)",
      extfreq_R < 3.75 ~ "Moderate (~2 yrs)",
      extfreq_R < 4.5  ~ "Seasonal yearly",
      TRUE             ~ "Constant"
    )
  ) %>%
  mutate(
    extfreq_rebin = factor(
      extfreq_rebin,
      levels = c("Rare", "Occasional", "Frequent"),
      ordered = TRUE
    ),
    extfreq_rebin_large = factor(
      extfreq_rebin_large,
      levels = c(
        "Rare/Absent",
        "Low (3–10 yrs)",
        "Moderate (~2 yrs)",
        "Seasonal yearly",
        "Constant"
      ),
      ordered = TRUE
    )
  )


ggplot(fd_extfreq, aes(x = extfreq_rebin, y = disaster_h9a_sev_exposure_30_IA)) +
  geom_boxplot()

```

```{r}
ggplot(fd_extfreq, aes(x = disaster_h9a_sev_exposure_30_IA, y = extfreq_R)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

# sensitivity analysis
fd_extfreq$z_sev <- scale(fd_extfreq$disaster_h9a_sev_exposure_30_IA)

fd_extfreq_trim <- fd_extfreq[abs(fd_extfreq$z_sev) <= 2, ]


ggplot(fd_extfreq_trim, aes(x = disaster_h9a_sev_exposure_30_IA, y = extfreq_R)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

```

Really not seeing any sort of relationship here and it's a bit hard to decipher given the scaling of the warfare variables.

## Intrfreq
```{r}
fd_intrfreq <- ds[complete.cases(ds[, c("disaster_h9a_sev_exposure_30_IA", "intrfreq_R")]), ]
```

```{r}
ggplot(fd_intrfreq, aes(x = disaster_h9a_sev_exposure_30_IA, y = intrfreq_R)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

# sensitivity analysis
fd_intrfreq$z_sev <- scale(fd_intrfreq$disaster_h9a_sev_exposure_30_IA)

fd_intrfreq_trim <- fd_intrfreq[abs(fd_intrfreq$z_sev) <= 2, ]


ggplot(fd_intrfreq_trim, aes(x = disaster_h9a_sev_exposure_30_IA, y = intrfreq_R)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

```

```{r}
mod_fd_intrfreq <- brm(
  formula = intrfreq_R ~ disaster_h9a_sev_exposure_30_IA,
  data = fd_intrfreq_trim,
  family = gaussian(),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),  # Weakly informative normal priors for the coefficients
    prior(cauchy(0, 1), class = "Intercept")  # Weakly informative Cauchy prior for the intercept
  )
)

summary(mod_fd_intrfreq)
plot(mod_fd_intrfreq, type = "coef")

conditional_effects_plot <- conditional_effects(mod_fd_intrfreq)
plot(conditional_effects_plot)
```

```{r}
# in the our better nature paper, daily food sharing was negatively associated with food destroying hazards
hypothesis(mod_fd_intrfreq, "disaster_h9a_sev_exposure_30_IA < 0") # they do!

draws2 <- as_draws_df(mod_fd_intrfreq)

# Plot for Sev
pfd_intrfreq <- draws2 %>%
  ggplot(aes(x = b_disaster_h9a_sev_exposure_30_IA)) +
  geom_density(fill = "purple", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  labs(
    title = "Overall Warfare Frequency",
    x = expression(beta ~ "(Severity Exposure to Food Destroying Hazards)"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16, margin = margin(b = 10)),
    axis.title = element_text(face = "bold")
  )

pfd_intrfreq
```


