---
title: "testing-labor-sharing-across-fd-hazards"
format: html
---

```{r}
library(tidyverse)
library(brms)
```

# Testing Daily and Seasonal Labor Sharing Across Food Destroying & Non-Food Destroying Hazards

```{r}
ds_FA <- read_csv("sharing-dataset-for-analysis.csv")

ds_FA <- ds_FA %>%
  mutate(
    normative_ind = if_else(normative_est_count_30 > 0, 1, 0),
    normative_ind_IA = if_else(normative_est_count_30_IA > 0, 1, 0)
  )

table(ds_FA$normative_ind)
```

## Seasonal Labor Sharing
```{r}
cor.test(
  ds_FA$LS3_Res_IA_2,
  ds_FA$ea033,
  use = "complete.obs",
  method = "spearman"
)

cor.test(
  ds_FA$LS3_Res_IA_2,
  ds_FA$class_strat,
  use = "complete.obs",
  method = "spearman"
)

cor.test(
  ds_FA$LS3_Res_IA_2,
  ds_FA$community_size,
  use = "complete.obs",
  method = "spearman"
)

cor.test(
  ds_FA$LS3_Res_IA_2,
  ds_FA$intensity_agricult,
  use = "complete.obs",
  method = "spearman"
)

cor.test(
  ds_FA$disaster_fd_sev_exposure2.5_30,
  ds_FA$disaster_h9a_sev_exposure_30,
  use = "complete.obs",
  method = "spearman"
)
```
### Food destroying
```{r}
data_clean_LS3 <- ds_FA[complete.cases(ds_FA[, c("disaster_fd_sev_exposure2.5_30", "LS3_Res_IA_2")]), ]

ggplot(ds_FA, aes(x = disaster_h9a_sev_exposure_30, y = LS3_Res_IA_2)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```

```{r}
mod_LS3 <- brm(
  formula = LS3_Res_IA_2 ~ disaster_fd_sev_exposure2.5_30,
  data = data_clean_LS3,
  family = bernoulli(link = "logit"),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),  # Weakly informative normal priors for the coefficients
    prior(cauchy(0, 1), class = "Intercept")  # Weakly informative Cauchy prior for the intercept
  )
)

mod_LS3_IA <- brm(
  formula = LS3_Res_IA_2 ~ disaster_fd_sev_exposure2.5_30_IA,
  data = data_clean_LS3,
  family = bernoulli(link = "logit"),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  prior = c(
    prior(normal(0, 2.5), class = "b"),  # Weakly informative normal priors for the coefficients
    prior(cauchy(0, 1), class = "Intercept")  # Weakly informative Cauchy prior for the intercept
  )
)


summary(mod_LS3)
plot(mod_LS3, type = "coef")

conditional_effects_plot <- conditional_effects(mod_S3)
plot(conditional_effects_plot)
```

```{r}
hypothesis(mod_LS3, "disaster_fd_sev_exposure2.5_30 < 0")

drawLS3 <- as_draws_df(mod_LS3)


x_vals <- drawLS3$b_disaster_fd_sev_exposure2.5_30
x_lim <- max(abs(x_vals), na.rm = TRUE)

post_prob <- mean(x_vals < 0, na.rm = TRUE)

pfdLS3 <- drawLS3 %>%
  ggplot(aes(x = b_disaster_fd_sev_exposure2.5_30)) +
  geom_density(fill = "#ED7D31", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  coord_cartesian(xlim = c(-x_lim, x_lim)) +
  annotate(
    "text",
    x = x_lim * 0.95,
    y = Inf,
    label = paste0("Post. Prob = ", round(post_prob * 100, 1), "%"),
    hjust = 1,
    vjust = 1.5,
    size = 5
  ) +
  labs(
    x = expression(beta ~ "(Food destroying hazards weighted by severity)"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16, margin = margin(b = 10)),
    axis.title = element_text(face = "bold")
  )

pfdLS3
```

```{r}
hypothesis(mod_LS3_IA, "disaster_fd_sev_exposure2.5_30_IA < 0")

drawLS3_IA <- as_draws_df(mod_LS3_IA)


x_vals <- drawLS3_IA$b_disaster_fd_sev_exposure2.5_30_IA
x_lim <- max(abs(x_vals), na.rm = TRUE)

post_prob <- mean(x_vals < 0, na.rm = TRUE)

pfdLS3_IA <- drawLS3_IA %>%
  ggplot(aes(x = b_disaster_fd_sev_exposure2.5_30_IA)) +
  geom_density(fill = "#ED7D31", alpha = 0.7) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  coord_cartesian(xlim = c(-x_lim, x_lim)) +
  annotate(
    "text",
    x = x_lim * 0.95,
    y = Inf,
    label = paste0("Post. Prob = ", round(post_prob * 100, 1), "%"),
    hjust = 1,
    vjust = 1.5,
    size = 5
  ) +
  labs(
    x = expression(beta ~ "(Food destroying hazards weighted by severity (IA))"),
    y = "Density"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold", size = 16, margin = margin(b = 10)),
    axis.title = element_text(face = "bold")
  )

pfdLS3_IA
```


### Non-Food destroying

```{r}
sevnfd_LS3 <- ds_FA[complete.cases(ds_FA[, c("disaster_nonfd_sev_exposure2.5_30", "LS3_Res_IA_2")]), ]

ggplot(data_clean_LS3, aes(x = nonfd_2.5_freq_30, y = LS2_Res_IA_2)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

```
Don't look like much.

## Daily Labor Sharing

```{r}
cor.test(
  ds_FA$LS2_Res_IA_2,
  ds_FA$ea033,
  use = "complete.obs",
  method = "spearman"
)

cor.test(
  ds_FA$LS2_Res_IA_2,
  ds_FA$class_strat,
  use = "complete.obs",
  method = "spearman"
)

cor.test(
  ds_FA$LS2_Res_IA_2,
  ds_FA$community_size,
  use = "complete.obs",
  method = "spearman"
)

cor.test(
  ds_FA$LS2_Res_IA_2,
  ds_FA$intensity_agricult,
  use = "complete.obs",
  method = "spearman"
)
```
### Food destroying (2.5)
```{r}
data_clean_S2 <- ds_FA[complete.cases(ds_FA[, c("disaster_fd_sev_exposure2.5_30", "S2_Resolved_IA_TR")]), ]

ggplot(data_clean_LS3, aes(x = disaster_h9a_sev_exposure_30, y = LS2_Res_IA_2)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

```
Doesn't look like much...

### Non-food destroying
```{r}
ggplot(data_clean_LS3, aes(x = disaster_nonfd_sev_exposure2.5_30_IA, y = LS2_Res_IA_2)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```
also doesn't look like much.

# Looking at all hazards variables

## Seasonal labor sharing

### Food destroying vars
```{r}
ggplot(data_clean_LS3, aes(x = allhazards_fd_sev_exposure2.5_30, y = LS3_Res_IA_2)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(data_clean_LS3, aes(x = allhazards_fd_sev_exposure2.5_30_IA, y = LS3_Res_IA_2)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(data_clean_LS3, aes(x = allhazards_fd_sev_exposure2_30, y = LS3_Res_IA_2)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(data_clean_LS3, aes(x = allhazards_fd_sev_exposure2_30_IA, y = LS3_Res_IA_2)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(data_clean_LS3, aes(x = allhazards_H9a_sev_exposure_30, y = LS3_Res_IA_2)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
ggplot(data_clean_LS3, aes(x = allhazards_H9a_sev_exposure_30_IA, y = LS3_Res_IA_2)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```


### Non fd vars
```{r}
ggplot(data_clean_LS3, aes(x = allhazards_nonfd_sev_exposure2.5_30, y = LS3_Res_IA_2)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
ggplot(data_clean_LS3, aes(x = allhazards_nonfd_sev_exposure2.5_30_IA, y = LS3_Res_IA_2)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(data_clean_LS3, aes(x = allhazards_nonfd_sev_exposure2_30, y = LS3_Res_IA_2)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
ggplot(data_clean_LS3, aes(x = allhazards_nonfd_sev_exposure2_30_IA, y = LS3_Res_IA_2)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```
## Daily Labor Sharing
### Food destroying
```{r}
ggplot(data_clean_LS3, aes(x = allhazards_fd_sev_exposure2.5_30, y = LS2_Res_IA_2)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(data_clean_LS3, aes(x = allhazards_fd_sev_exposure2.5_30_IA, y = LS2_Res_IA_2)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(data_clean_LS3, aes(x = allhazards_fd_sev_exposure2_30, y = LS2_Res_IA_2)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(data_clean_LS3, aes(x = allhazards_fd_sev_exposure2_30_IA, y = LS2_Res_IA_2)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(data_clean_LS3, aes(x = allhazards_H9a_sev_exposure_30, y = LS2_Res_IA_2)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
ggplot(data_clean_LS3, aes(x = allhazards_H9a_sev_exposure_30_IA, y = LS2_Res_IA_2)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```


### Non fd vars
```{r}
ggplot(data_clean_LS3, aes(x = allhazards_nonfd_sev_exposure2.5_30, y = LS2_Res_IA_2)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
ggplot(data_clean_LS3, aes(x = allhazards_nonfd_sev_exposure2.5_30_IA, y = LS2_Res_IA_2)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")

ggplot(data_clean_LS3, aes(x = allhazards_nonfd_sev_exposure2_30, y = LS2_Res_IA_2)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
ggplot(data_clean_LS3, aes(x = allhazards_nonfd_sev_exposure2_30_IA, y = LS2_Res_IA_2)) +
  geom_jitter(height = 0.05, alpha = 0.6) +
  geom_smooth(method = "loess", se = FALSE, color = "#66c2a4")
```


